---
title: "rcces"
output: github_document
---

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


`rcces` is includes functions that could be useful in reading in and analyzing data from the [CCES](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/II2DB6). Currently it is just a bundle of personal functions, not designed for distribution. For the latter, you may be interested in the other repositories listed below.


## Installation

The package will not be on CRAN. You can install it via:

```{r, eval = FALSE}
pak::pkg_install("kuriwaki/rcces")
```

Or, equivalently,

```{r, eval = FALSE}
remotes::install_github("kuriwaki/rcces")
```


## Related Packages

- [`ccesMRPprep`](https://www.shirokuriwaki.com/ccesMRPprep/reference/index.html) includes functions and documentation on how to download and standardized data. It is geared towards standardization for MRP, but some of the vignettes and documentation use common standardization procedures and document features of the MRP dataset. 
- [`ccesMRPrun`](https://github.com/kuriwaki/ccesMRPrun/tree/master/R) includes functions to fit a multilevel model and poststratify to a target (computed by `ccesMRPprep`).
- [`cces_cumulative`](https://github.com/kuriwaki/cces_cumulative) includes code that shows how the cumulative Common Content was created. The cumulative dataset is a stacked version of key columns in the year-specific CCES, and can be used as a base dataset into which year-specific questions can be merged back. 
